Verifying Demonstrations

### 2019-12-02 paper/DBSchnorr-n-bit.tex
Adds sketch of l-bit problem with commitments

\paragraph*{The general \(l\)-bit problem}

@@

>>>>

\paragraph*{The unconditional \(l\)-bit problem}

@@

\paragraph*{The \(l\)-bit problem with commitments}

The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
g^{r_i}\) and a commitment to \(\alpha\) in the form of \(A = g^\alpha\).
This means that
\begin{align*}
  R = A^{-c'} g^{s'} &= A^{-c'} g^{s'[0] 2^0 + \dotsb + s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'[0] 2^0} \dotsb g^{s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'_{\text{known}}} g^{s'_{\text{unknown}}}.
\end{align*}
We will now show that finding \(s'_\text{unknown}\) is as hard as finding 
discrete logarithms.

\begin{definition}[\Acl*{DLP}]
  Let \(g\) be a generator for a group of prime order~\(q\).
  Given \(g, q, A = g^\alpha\), compute \(\alpha\).
\end{definition}

\begin{definition}[DB-Schnorr Problem]%
  \label{DBSchnorr-problem}
  Let \(g\) be a generator for a group of prime order~\(q\).
  Give \(g, q, R = g^\rho A = g^\alpha\) to the adversary.
  Let the adversary choose \(c\) and additionally give him \(\hat s\) such that 
  \(\hat s\) are the \(l\) \emph{least significant} bits of \(s = \rho + 
  c\alpha \pmod q\).
  The adversary wins if he returns \(\hat s'\) such that \(\hat s + \hat s' = s 
  \pmod q\).
\end{definition}

\begin{lemma}
  Given an algorithm~\(\algA_{\DBS}\) that solves the DB-Schnorr Problem 
  (\cref{DBSchnorr-problem}) with probability \(\epsilon\), we can construct an 
  algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 
  \((1-\frac{1}{2^{X}}) \epsilon\).
\end{lemma}

\begin{proof}
  We will now construct the algorithm \(\algA_{\text{DL}}\) given the algorithm 
  \(\algA_{\DBS}\).
  Given \(g, q, A_{\text{DL}}\):
%  Let \(\rho\rgets \ZZ_q\), \(c\gets \algA_{\DBS}(R, A_{\DBS})\), where \(R = 
%  g^\rho\) and \(A_{\DBS} = g^\alpha\).
  Choose \(s\rgets \ZZ_q\) and let \(\rho\gets s - c\alpha\)
\end{proof}
